\documentclass{truonggiangit793}

\setname{Pham}{Truong Giang}
\setgender{\textbf{Gender:} Male}
\setdob{\textbf{Date of birth:} April 02, 2001}
\setmobile{\textbf{Mobile:} +84 702 907 154}
\setaddress{\textbf{Address:} District 7, HCM City}
\setmail{\textbf{Email:} truonggiangit793@gmail.com}
\setposition{\emph{Be unique, be yourself!}} %ignored
\setgithubaccount{https://github.com/truonggiangit793}
\setfacebookaccount{https://www.facebook.com/truonggiangit793}
\setlinkedinaccount{https://linkedin.com/in/truonggiangit793}
\setthemecolor{teal}

\begin{document}
\headerview
\vspace{1ex}

%Summary
\addblocktext{Objective}{I am an enthusiastic and dedicated individual from Vietnam, eager to pursue a career as a professional programmer. With a natural aptitude for learning, I quickly grasp new concepts and adapt to emerging technologies. My ability to apply my knowledge to practical projects showcases my creativity and problem-solving skills. I am highly motivated to contribute to the success of an organization, valuing teamwork and collaboration.}

%Education
\section{Education} 
%
\datedexperience{Ton Duc Thang University}{October 2019 - Now} 
\explanation{Bachelor of Information Technology} 
\explanationdetail{\coloredbullet\ Major: Computer Networks and Data Communication.}
  
%Experience
\section{Activities}
%
\datedexperience{IT Help-desk Volunteer}{August 2020 - March 2022}
\explanation{Work at: VIETNAM FINLAND INTERNATIONAL SCHOOL (VFIS)}
\explanationdetail{\coloredbullet\ Give staff and student's parents a helping hand with computer and student portal problems.}
\explanationdetail{\coloredbullet\ Check and keep computer rooms always in good maintained.} 
\explanationdetail{\coloredbullet\ Recognition and Gains: Achievement recognition results of training evaluation.} 
%
\datedexperience{Designer}{October 2019 - November 2020} 
\explanation{Work at: ALUMNI COMMITTEES ASSOCIATION (ACA) - TDTU} 
\explanationdetail{\coloredbullet\ Work as a photographer and designer in media team.}
\explanationdetail{\coloredbullet\ Recognition and Gains: Achievement recognition results of training evaluation.}
    
%Skills
\section{Skills}
%
\newcommand{\skillone}{\createskill{Programming languages:}{ JavaScript \cpshalf Python \cpshalf PHP \cpshalf Java }}
%
\newcommand{\skilltwo}{\createskill{Library \& Frameworks:}{ VueJS \cpshalf ReactJS \cpshalf ExpressJS \cpshalf React Native \cpshalf JQuery \cpshalf Tailwind \cpshalf Bootstrap }}
%
\newcommand{\skillthree}{\createskill{Languages:}{\textbf{\emph{Native:}} Vietnamese \cpshalf \textbf{\emph{Other:}} English (Reading documents \& basic communication) }}
%
\newcommand{\skillfour}{\createskill{Design:}{ Adobe Photoshop \cpshalf Adobe Illustrator \cpshalf Figma }}
%
\newcommand{\skillfive}{\createskill{Office:}{ Microsoft Word \cpshalf Microsoft Excel \cpshalf Microsoft PowerPoint }}
%
\newcommand{\skillsix}{\createskill{Others:}{ Docker \cpshalf GIT \cpshalf Linux \cpshalf MongoDB \cpshalf MySQL }}
%
\createskills{\skillone,\skilltwo,\skillthree,\skillfour,\skillfive,\skillsix}
%
%Projects
\section{Projects}
%
\datedexperience{Noiz Music Player}{}
\explanationdetail{\coloredbullet\ \textbf{\emph{Github repository:}} \href{https://github.com/truonggiangit793/noiz-music}{https://github.com/truonggiangit793/noiz-music}}
\explanationdetail{\coloredbullet\ \textbf{\emph{Description:}} This is an entertainment website for music lovers. At Noiz Music, I believe that music is not just a form of entertainment but a way of life. Song library is based on the renowned ZingMp3 API, it's easy for you to discover new artists, create playlists, and share your favorite tracks with friends and family.}
\explanationdetail{\coloredbullet\ \textbf{\emph{Team size:}} 1.}
\explanationdetail{\coloredbullet\ \textbf{\emph{Technologies:}} ExpressJS for API, VueJS for front-end, Docker.}
\explanationdetail{\coloredbullet\ \textbf{\emph{My responsibilities:}} Developer, UI design, optimize code, bug fixing.}
%
\createfootnote{1/2}
%
\pagebreak
%
\section{Projects}
%
\datedexperience{Point of Sale - Store system}{}
\explanationdetail{\coloredbullet\ \textbf{\emph{Github repository:}} \href{https://github.com/truonggiangit793/store-system}{https://github.com/truonggiangit793/store-system}}
\explanationdetail{\coloredbullet\ \textbf{\emph{Description:}} This project explores the application of IT in retail business through the analysis and design of a retail store system. This innovative approach promises convenience, efficiency, and improved management, while enhancing our vocational skills and addressing common challenges.}
\explanationdetail{\coloredbullet\ \textbf{\emph{Team size:}} 2.}
\explanationdetail{\coloredbullet\ \textbf{\emph{Technologies:}} ExpressJS for back-end, VueJS for front-end, MongoDB for database.}
\explanationdetail{\coloredbullet\ \textbf{\emph{My responsibilities:}} Developer, UI design, optimize code, bug fixing.}
%
\datedexperience{Barcode scanner - Mobile application}{}
\explanationdetail{\coloredbullet\ \textbf{\emph{Github repository:}} \href{https://github.com/truonggiangit793/barcode-scanner-mobile-app}{https://github.com/truonggiangit793/barcode-scanner-mobile-app}}
\explanationdetail{\coloredbullet\ \textbf{\emph{Description:}} The application of barcode scanning in managing near-expiry products at convenience stores: Instead of manually recording barcode numbers, expiration dates, and quantities, our app allows employees to scan product barcodes using their phone's camera. The system displays the product information, and employees simply input expiration dates and quantities, saving time and eliminating the need for manual data entry. Additionally, store managers can easily download an Excel file without the tedious task of manually inputting data.}
\explanationdetail{\coloredbullet\ \textbf{\emph{Team size:}} 1.}
\explanationdetail{\coloredbullet\ \textbf{\emph{Technologies:}} ExpressJS for API, MongoDB for database, React Native for mobile app.}
\explanationdetail{\coloredbullet\ \textbf{\emph{My responsibilities:}} Developer, UI design, optimize code, bug fixing.}
%
\datedexperience{Facebook AI Chatbot - Webhook}{}
\explanationdetail{\coloredbullet\ \textbf{\emph{Github repository:}} \href{https://github.com/truonggiangit793/facebook-chatbot}{https://github.com/truonggiangit793/facebook-chatbot}}
\explanationdetail{\coloredbullet\ \textbf{\emph{Description:}} This project used for building a facebook chatbot. By providing OpenAI API key, this webhook can response any prompt by user then send the anwser to facebook via Messenger.}
\explanationdetail{\coloredbullet\ \textbf{\emph{Team size:}} 1.}
\explanationdetail{\coloredbullet\ \textbf{\emph{Technologies:}} ExpressJS for API, OpenAI API.}
\explanationdetail{\coloredbullet\ \textbf{\emph{My responsibilities:}} Developer, UI design, optimize code, bug fixing.}
%
\datedexperience{Youtube clean mode - Chrome extension}{}
\explanationdetail{\coloredbullet\ \textbf{\emph{Github repository:}} \href{https://github.com/truonggiangit793/youtube-clean-mode-extension}{https://github.com/truonggiangit793/youtube-clean-mode-extension}}
\explanationdetail{\coloredbullet\ \textbf{\emph{Description:}} This extension allows users to customize their viewing experience by hiding certain elements of the page. Specifically, this extension offers the ability to hide the title of the current video, the controller, and suggested videos, as well as a theater mode that highlights the video frame by blurring the background.}
\explanationdetail{\coloredbullet\ \textbf{\emph{Team size:}} 1.}
\explanationdetail{\coloredbullet\ \textbf{\emph{My responsibilities:}} Developer, UI design, optimize code, bug fixing.}
%

%Footnote
\createfootnote{2/2}
\end{document}